Artificial Neural Network based critical conditions for Dynamic Recrystallization of Medium Carbon Steel and Application

### 2023-08-29 Article.tex
Last comments taken into account and one ref added

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process while hot-compressing steel.
To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
We also employed an artificial neural network (ANN) to model thermo-visco-plastic behavior with a flow law.
The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations.
The Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
The comparison revealed a strong correlation between simulation and experiment.
The study investigated the impact of temperature, strain, and strain rate on DRX evolution.
The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}

@@

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation.
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Barnett \eal \cite{barnett2000predicting}\OP{M.J. suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation. You could find review papers about this.)} determined the critical strain for the initiation of DRX using the kinetics of static recrystallization (SRX), which was adapted to allow SRX to begin before the end of deformation.
This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volumetric fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

@@

The experimental tests used in this work are identical to those previously published by Tize Mha \eal \cite{TizeMha-2023}.
For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
Nonetheless, we will outline the key aspects necessary to comprehend the suggested methodology.
%The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
%At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
%In this new study, the ANN model will be used for predicting dynamic recrystallization, as explained in the introduction.
%It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.

@@

The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
\begin{table}[H]
\centering
\caption{Chemical composition of medium carbon steel. Fe = balance.}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\toprule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.

@@

The flow stress ($\sigma$) increases as the strain rate ($\mdot\varepsilon$) rises but decreases as the temperature ($T$) increases.
Notably, the strain also affects the flow stress.
At the lowest strain rates, the flow stress increases up to $\sigma_p$ as the strain approaches a value of about $\varepsilon_p=0.2$ to $0.3$.
Then, it decreases to maintain a relatively constant value throughout the entire test.
Conversely, at strain rates above $1~\ps$, the flow stress increases steadily throughout the test.
The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
Furthermore, this frictional effect becomes more apparent as lubrication reduces over time.

@@

Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a plateau.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the deformation parameters (deformation rate, temperature, and deformation) condition dynamic recrystallization (DRX), which can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling pre- and post-critical deformation.
In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind.

In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the DRX model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of forecasting the volume fraction of dynamic recrystallization.

%----------------------------------------------------------------------------------
\subsection{DRX model's parameters identification\label{subsec:DRXParameters}}
%----------------------------------------------------------------------------------

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volumetric fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volumic fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

@@

The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX}.
The figure compares the experimentally measured $X_{drx}$ with the predicted values under the tested strain rates and temperatures. \OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data. Also check that the color of the dots is on in Figure 7.}
The curves illustrate the changes in predicted volume fractions of DRX with plastic strain.
It is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
At a constant temperature and strain, the DRX volume fraction increases with decreasing strain rate.
Conversely, at a fixed strain rate and strain, the DRX volume fraction increases with rising temperature.
The difference between the predicted and experimental volume fractions of DRX is insignificant, confirming the suitability of the proposed approach for DRX prediction in the studied superalloy under various forming conditions.
The reduction of DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to forming temperature and strain rate.
Dynamic recrystallization is prone to occur at high forming temperatures and low strain rates due to increased grain boundary mobility.
However, because of the limited mobility of grain boundaries, the rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
The validation of the model used in the study, as evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation section.

@@

We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volumetric fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more profound comprehension of the complex processes occurring during deformation.
Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests.
This allowed us to capture the process's response to varying conditions without bias.
By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.

It is noteworthy that although our research represents a significant milestone, it also presents opportunities for future exploration.
Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace.

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{This study presents a novel and thorough approach to comprehending and simulating the DRX process \textcolor{red}{during} hot-compressing steel.
To achieve this goal, we studied the high-temperature deformation behavior of a medium-carbon steel through hot compression testing on a Gleeble-3800 thermomechanical simulator over a broad range of strains, strain rates, and temperatures.
We also employed an artificial neural network (ANN) to model thermo-visco-plastic behavior with a flow law.
The precision of quantifying DRX volume fraction is dependent on critical conditions, which are essential for both analytical model evaluation and numerical implementation in finite element software.
This study proposes a second ANN, serving as a universal approximator, to fit the data required for DRX critical condition calculations \textcolor{red}{whereas the} Johnson-Mehl-Avrami-Kohnogorov (JMAK) model served as an analytical tool to estimate the DRX volume fraction, which underwent validation through experimental measurements.
A numerical implementation of the JMAK model was conducted in ABAQUS software and compared against experimental data by means of microstructure analysis.
The comparison revealed a strong correlation between simulation and experiment.
The study investigated the impact of temperature, strain, and strain rate on DRX evolution.
The findings showed that DRX increases with rising temperature and strain, but decreases with increasing strain rate.}

@@

Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, when undergoing plastic deformation (\textcolor{red}{Meaning : Dynamic recrystallization is a process observed in specific materials, mainly metals and alloys, as they undergo the process of plastic deformation}).
It is a phenomenon frequently seen in hot working operations, including hot rolling, hot forging, and hot extrusion.
When a metal or alloy undergoes significant plastic deformation at high temperatures, its existing grain structure is disrupted.
During the deformation process, new, smaller grains are formed, which is referred to as dynamic recrystallization (DRX).
DRX differs from static recrystallization (SRX) which takes place when there is no deformation applied on the material.
The amount of energy stored in the metal due to plastic deformation is the driving force behind the DRX process.
Typically, the newly formed grains are much smaller than the original grains of the undeformed material.
Their growth is accelerated by the stored energy and high temperatures.
DRX provides several benefits in the hot forming process by refining the grain size, enhancing the mechanical properties of the material, including strength and toughness \cite{shen2021effect}.

As the occurence of the DRX softens the material, the deformation loads during hot deformation must be adjusted from one pass to another to have more accurate prediction of DRX.
Therefore, understanding the critical conditions for dynamic recrystallization (DRX) is important for modeling industrial processes.
However, the extent of DRX is influenced by factors such as material composition, deformation temperature, strain rate, and strain.
By optimizing the parameters, engineers can attain the desired microstructures and mechanical properties in the final product.
Various techniques have been proposed by researchers to establish DRX's critical conditions such as metallography \cite{babu2022implication} \textcolor{red}{That is an experimental method to evalute DRX volume fraction}.
However, this technique requires extensive sampling before and after reaching the critical deformation point at which the material experiences recovery and recrystallization processes, resulting in the formation of new grains and a decrease in the average grain size.
Additionally, the cooling phase sometimes entails phase changes (depending the material's type) from the hot working temperature, which alter the deformed structure, rendering the metallographic analysis complex.
Hence, simpler techniques such as the development of analytical models are required to determine DRX initiation.
In this regard, multiple studies have been carried out aiming to analytically identify the initiation of DRX.
For instance, Yan Peng \eal \cite{peng2022dynamic}\OP{M.J. suggested that you use another reference (I suggest to use another reference that is only about analytical models for DRX initiation. You could find review papers about this.)} \textcolor{red}{Done !} determined the critical strain and critical stress for the DRX's initiation based on the method proposed by Najafizadeh and Jonas \cite{Najafizadeh-2006} to establish a DRX kinetic model for the hot-rolled condition based on the relationship between the characteristic parameters of DRX and temperature and strain rate. This approach defines the critical stress required for the initiation of DRX during deformation.
According to Gottstein \eal \cite{gottstein2004prediction}, the critical strain for initiating DRX can also be predicted based on a work hardening model of dislocation density.
The onset of dynamic recrystallization (DRX) may be identified through the inflection point in the strain hardening rate $\theta(\sigma)=\frac{\partial \sigma}{\partial \varepsilon}$ where $\sigma$ is the stress and $\varepsilon$ is the strain.

The DRX phenomenon, based on the inflection point, was first studied by Ryan and McQueen \cite{ryan1989dynamic, ryan1990dynamic, ryan1990flow}.
They observed the appearance of an inflection point on the $\theta(\sigma)$ curve before the peak stress $\sigma_p$ and attributed the beginning of DRX and the critical conditions to this point.
Later, Poliak and Jonas \cite{Poliak-1996,Poliak-2003,Poliak-2003-2,jonas2003critical} confirmed the hypothesis of DRX describing the inflection point by demonstrating that it is associated with thermodynamic energy released during dislocation movements and the combinaison between the current dislocations with the previous one leads to the DRX's initiation.
Najafizadeh and Jonas \cite{Najafizadeh-2006} simplified Poliak and Jonas' thermodynamic model using an analytical technique to determine the critical conditions for initiating DRX.
Their widely-used approach relies on a third-degree polynomial to describe the curve $\theta(\sigma)$ and the second derivative to identify the critical stress $\sigma_c$ and strain $\varepsilon_c$.
Once calculated, the critical conditions serve as input data for the Johnson-Mehl-Avrami-Kolmogorov (JMAK) model \cite{Avrami-1939}.
This model is commonly used to estimate the volume fraction of dynamic recrystallization $X_{drx}$ during hot working.
Li \eal \cite{li2015experimental} investigated the DRX properties of micro-alloyed plastic molding steel by using the Avrami kinetics model equation and the Estrin and Mecking mathematical model \cite{estrin1984unified,mecking1981kinetics} to determine the Avrami equation coefficients.

@@

The experimental tests used in this work are identical to those previously published by Tize Mha \eal \cite{TizeMha-2023}.
For additional information, readers can refer to the publications by our research group \cite{Pantale-2021, Pantale-2023}.
Nonetheless, we will outline the key aspects necessary to \textcolor{red}{understand} the suggested methodology.
%The first publication focused on developing a constitutive law capable of predicting material flow, for which a comparative study between 5 analytical models and a neural network-based model was conducted.
%At the conclusion of this comparative study, the Artificial Neural Network (ANN) model proved to be the best performing.
%In this new study, the ANN model will be used for predicting dynamic recrystallization, as explained in the introduction.
%It's worth noting that the ANN model identified in the first publication will also be employed for managing the plastic behavior of the material.

@@

The material used for this study is a medium-carbon steel with the chemical composition presented in Table \ref{tab:Composition}.
\begin{table}[H]
\centering
\caption{Chemical composition of medium carbon steel. Fe = balance.}
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\toprule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
\textcolor{red}{Those who want to go deep could read the previous paper as experimental setup is more explained there}

Hot compression tests were conducted on cylinders with an initial diameter of $\phi=10$~mm and a height of $h=15$~mm using a Gleeble-3800 thermomechanical simulator.
The tests were conducted at 5 temperature levels (ranging from $1050\celsius$ to $1250\celsius$) and 6 strain rates (ranging from $0.001~\ps$ to $5~\ps$).
The imposed displacement was set to $d=6$~mm, resulting in a reduction of $40\%$ of the initial height.
To reduce friction during testing, thin tantalum sheets were used as a lubricant on the contact surface of the anvils and specimens.
In order to remove thermal gradients, the samples were heated at a speed of $2$\celsius/s until reaching a temperature of $1260\celsius$, then held at that temperature for $5$~minutes.
They were subsequently cooled down to the test temperature at a speed of $1$\celsius/s and left at a consistent temperature for $1$~minute prior to being formed.
During compression, the sample temperature is maintained at a constant level through the machine's thermal control system.
Subsequently, the structure is frozen at a fast pace in order to preserve the microstructure for future analysis.

@@

The flow stress ($\sigma$) increases as the strain rate ($\mdot\varepsilon$) rises but decreases as the temperature ($T$) increases.
Notably, the strain also affects the flow stress.
At the lowest strain rates, the flow stress increases up to $\sigma_p$ as the strain approaches a value of about $\varepsilon_p=0.2$ to $0.3$.
Then, it decreases to maintain a relatively constant value throughout the entire test.
Conversely, at strain rates above $1~\ps$, the flow stress increases steadily throughout the test.
The nominal rise in stress observed at low strain rates with large strain values is attributed to friction between the sample and anvil during testing, as noted by Galos \eal \cite{Galos-2022}.
Furthermore, this frictional effect becomes more apparent as lubrication reduces over time . \textcolor{red}{Previous paper !}

@@

Dynamic recrystallization is a significant phenomenon for regulating a material's microstructural and mechanical properties during hot working.
In some materials like aluminum, DRX can counterbalance work hardening, leading to a rapid emergence of a \textcolor{red}{threshold}.
However, in many austenitic steels, the kinetics of restoration are feeble, causing DRX to activate at a critical strain accumulation condition.
Due to DRX's significant impact on the material's flow stress at high temperatures, it unavoidably affects the material's microstructure following hot working.
Therefore, it is critical to accurately predict the start of DRX to effectively characterize the material.
Several factors, such as the chemical composition of the material, the grain size before deformation, the mode of deformation, and the \textcolor{red}{physical} parameters (strain rate, temperature, and strain) condition dynamic recrystallization (DRX), which \textcolor{red}{Which is for DRX} can only be triggered once the critical deformation is reached and can be determined via metallography.
However, this technique necessitates extensive sampling pre- and post-critical deformation.
In addition, the cooling phase alters the deformed structure during the descent from the hot working temperature, resulting in complicating metallographic analysis \textcolor{red}{During de cooling after deformation, there is phaseS changes in the microstruture which depends on the cooling rate and this can affects SRX}.
Hence simpler techniques, like developing analytical models have been implemented.
Several studies analyzing the initiation of DRX have been conducted with this objective in mind.

In this paper, we will use the Johnson-Mehl-Avrami-Kohnogorov (JMAK) phenomenological model \cite{Avrami-1939} to calculate the development of Dynamic Recrystallization (DRX) of the material during deformation.
The information obtained from the Gleeble thermosimulator will be used to identify the material flow law and the parameters of the DRX model.
We obtain the parameters of the JMAK model through a two-step process.
First, critical stresses and strains are determined using the ANN model to filter curves effectively.
Then, these critical values are used as input data to calculate parameters in the JMAK model, with the goal of \textcolor{red}{predicting} the volume fraction of dynamic recrystallization.

%----------------------------------------------------------------------------------
\subsection{DRX model's parameters identification\label{subsec:DRXParameters} \textcolor{red}{I think We can keep the paper organization like this but I understand what you mean ! thanks !}}
%----------------------------------------------------------------------------------

@@

The flow stress curve of the material is influenced by the rate of work hardening, which in turn is affected by dislocations within the free grains.
The predicted volume fraction of the dynamic recrystallization ($X_{drx}^{p}$) is estimated using the Avrami model \cite{wan2017experimental}, commonly known as the JMAK model, expressed by the following equation:
\begin{equation}
X_{drx}^{p} = 1 - \exp\left[ -k\left(\frac{\varepsilon - \varepsilon_c}{\varepsilon_p}\right)^{n_k}\right]
\label{eq:drxpred}
\end{equation}
With $\varepsilon_c$ and $\varepsilon_p$ as the critical and peak strain respectively; $k$ and $n_k$ as the model's parameters and the experimental equivalence of this volume fraction of DRX is given by :
\begin{equation}
X_{drx}^{e} = \frac{\sigma_p-\sigma}{\sigma_p-\sigma_{s}}
\label{eq:drxexp}
\end{equation}

@@

The critical conditions calculated by the Poliak method are used to provide the curves of $X_{drx}(\varepsilon)$ in Figure \ref{fig:nDRX} where comparison between experimental and prediction is made for strain rate $\mdot\varepsilon=0.001~\ps$ and three temperature ($1050^\circ$C, $1150^\circ$C and $1250^\circ$C). \OP{Write that comparison is only available for $\mdot\varepsilon=0.001~\ps$ because of availability of exp data. Also check that the color of the dots is on in Figure 7.} \textcolor{red}{Done !}
The curves illustrate the changes in predicted volume fractions of DRX with plastic strain and it is evident that the proportion of DRX is strongly affected by strain, temperature, and strain rate values.
The DRX kinetics exhibit an S-shaped curve, with the DRX volume fraction gradually increasing with strain.
At a constant temperature and strain, the DRX volume fraction increases with decreasing strain rate.
Conversely, at a fixed strain rate and strain, the DRX volume fraction increases with rising temperature.
The difference between the predicted and experimental volume fractions of DRX is insignificant, confirming the suitability of the proposed approach for DRX prediction in the studied superalloy under various forming conditions.
The reduction of DRX with increasing strain rate can be attributed to the sensitivity of the volume fraction of dynamic recrystallization to forming temperature and strain rate.
Dynamic recrystallization is prone to occur at high forming temperatures and low strain rates due to increased grain boundary mobility.
However, because of the limited mobility of grain boundaries, the rate of dynamic recrystallization is slow at low forming temperatures and high strain rates.
The validation of the model used in the study, as evidenced by the correlation between experimental and predicted results, supports the subsequent use of these findings in the simulation section.

@@

We used the predicted critical conditions to input into the JMAK model, resulting in the successful prediction of the volume fraction of DRX and providing valuable insights into the kinetics and mechanisms controlling recrystallization.
This incorporation establishes a connection between theoretical models and practical phenomena, ultimately leading to a more \textcolor{red}{deep} comprehension of the complex processes occurring during deformation.
Taking our investigation further, we integrated the JMAK model into the widely-used ABAQUS software to simulate the evolution of DRX during hot compression tests.
This allowed us to capture the process's response to varying conditions without bias \textcolor{red}{This is related to the architecture of the ANN model, nothing else}.
By comparing our simulation results with experimental data and using microstructure analysis, we have validated the accuracy of our simulations and confirmed the effectiveness of our predictive models.

It is noteworthy that although our research represents a significant milestone, it also presents opportunities for future exploration.
Further enhancing the accuracy and applicability of our predictions can be achieved by fine-tuning our model, expanding our dataset, and refining the integration process.
Moreover, the successful connection of theory, simulation, and experimentation offers a sturdy structure for addressing challenging material behavior issues in industries ranging from manufacturing to aerospace \textcolor{red}{or other applications}.
